### 2018-12-14 README.Rmd
fill out variable status chunks

<details><summary><b>Lake Characteristics</b> (`LAGOSNE`) </summary><p>

* [x] Lake depth
* [x] IWS area
* [x] IWS/Lake area
</p></details>

* Cropland Data Layer
    * IWS pasture types (forage or not)
    * IWS specific crops (corn, wheat, etc.)
    * IWS crop frequency/rotation
* gSSURGO
    * IWS wetland potential (as a proxy for tile drainage)
    * IWS soil organic carbon
    * IWS root zone depth
    * IWS lithology (sand %, clay %, etc.)
* USGS
    * IWS from county - manure, fertilizer, and deposition of N,P

>>>>

<details><summary><b>Crop Types</b> (`CDL`) </summary><p>

* [x] IWS pasture types (forage or not)
* [x] IWS specific crops (corn, wheat, etc.)
* [ ] IWS crop frequency/rotation
</p></details>

<details><summary>Soil types (`gSSURGO`) </summary><p>

* [x] IWS wetland potential (as a proxy for tile drainage)
* [x] IWS soil organic carbon
* [ ] IWS root zone depth
* [ ] IWS lithology (sand %, clay %, etc.)
</p></details>

<details><summary><b>Fertilizer and manure application data</b> (`USGS`) </summary><p>

* [x] IWS from county - manure, fertilizer, and deposition of N,P
</p></details>

<details><summary>Land use cover (`LAGOSNE`) </summary><p>

* [ ] Lake buffer LULC
* [x] IWS LULC 
</p></details>

<details><summary><b>Lake Characteristics and WQ</b> (`LAGOSNE`) </summary><p>

* [x] Lake depth
* [x] IWS area
* [x] IWS/Lake area
* [x] TP, TN, NO3
</p></details>
